opXRD: Open Experimental Powder X-ray Diffraction Database

### 2025-04-29 chapters/04_our_dataset.tex
Switch to Wiley Latex Template

\begin{table}[!htb]
\centering
\caption{\footnotesize Overview of the contributions to the opXRD database: The availability of the chemical composition, spacegroups, lattice parameters, and \replaced{the full structure}{atomic coordinates} of the underlying samples are indicated by the columns ``Comp.'', ``Spg.'', ``Lattice'' and ``\replaced{Full structure}{ Atom coords}.'' respectively.}
\label{tab:merged}
\scalebox{0.81}{
\begin{adjustbox}{center}
\begin{NiceTabular}{@{}llllllll@{}}[columns-width=1.2cm]
\toprule
\textbf{\ Institution} & \textbf{No. Patterns} & \textbf{Comp.} & \textbf{Spg.} & \textbf{Lattice} & \textbf{Full} & \textbf{Research Project} \\
& & & & & \textbf{Structure} & \\
\midrule
\ CNRS        &  1052         &  \cmark   & \pchk{85}  & \cmark    &   \pchk{85}   & Diffraction data extracted from the COD \\ 
\ USC         &  338          &  \cmark   & \cmark     & \pchk{90} &   \xmark   & Study of CuNi and CuAl alloys          \\
\ HKUST(GZ)   &  520          &  \pchk{4} & \pchk{4}   & \pchk{4}  &   \pchk{4}   & Phase identification dataset  \\ 
\ EMPA        &  770          & \cmark    & \pchk{63}  & \xmark    &   \xmark   & Metal halide perovskites, Zn-V-N libraries \\ 
\ INT         &  19,796       & \xmark    & \xmark     & \xmark    &   \xmark   & Compilation of various projects        \\ 
\ IKFT        &  64           & \xmark    & \xmark     & \xmark    &   \xmark   & Commercial catalysts, metals, metal oxides   \\ 
\ LBNL        &  70,012       & \xmark    & \xmark     & \xmark    &   \xmark   & Perovskites precursors, Mn-Sb-O system  \\ 
\midrule
\midrule
\added{\ $\sum$ Labeled}   & \added{2,179}  & \pchk{79}  & \pchk{66}  & \pchk{63}  & \pchk{42} & \added{Partially and fully labeled opXRD data} \\
\added{\ $\sum$ Unlabeled }& \added{90,373} & \xmark     & \xmark     & \xmark     & \xmark    & \added{Unlabeled opXRD data}\\
\bottomrule
\end{NiceTabular}
\end{adjustbox}}
\end{table}

@@

\begin{figure}[!htb]
    \centering
    \includegraphics[width=\linewidth]{figures/hist_CRYSTAL.png}
    \caption{\added{Histograms detailing properties of the structures underlying labeled diffraction patterns in the opXRD database: a) distribution of structures containing specified elements, b) distribution of structures containing spacegroups, c) distribution of No. atoms $N_{\text{atom}}$ contained in unit cell, d) distribution of unit cell volume $V_{\text{uc}}$.}}
    \label{fig:hist_CRYSTAL}
\end{figure}

>>>>

\begin{table}[!htb]
\centering
\caption{\footnotesize Overview of the contributions to the opXRD database: The availability of the chemical composition, spacegroups, lattice parameters, and \replaced{the full structure}{atomic coordinates} of the underlying samples are indicated by the columns ``Comp.'', ``Spg.'', ``Lattice'' and ``\replaced{Full structure}{ Atom coords}.'' respectively.}
\label{tab:merged}
\scalebox{0.9}{
\begin{adjustbox}{center}
\begin{NiceTabular}{@{}llllllll@{}}[columns-width=1.2cm]
\toprule
\textbf{\ Institution} & \textbf{No. Patterns} & \textbf{Comp.} & \textbf{Spg.} & \textbf{Lattice} & \textbf{Full Structure} & \textbf{Research Project} \\
\midrule
\ CNRS        &  1052         &  \cmark   & \pchk{85}  & \cmark    &   \pchk{85}   & Diffraction data extracted from the COD \\ 
\ USC         &  338          &  \cmark   & \cmark     & \pchk{90} &   \xmark   & Study of CuNi and CuAl alloys          \\
\ HKUST(GZ)   &  520          &  \pchk{4} & \pchk{4}   & \pchk{4}  &   \pchk{4}   & Phase identification dataset  \\ 
\ EMPA        &  770          & \cmark    & \pchk{63}  & \xmark    &   \xmark   & Metal halide perovskites, Zn-V-N libraries \\ 
\ INT         &  19,796       & \xmark    & \xmark     & \xmark    &   \xmark   & Compilation of various projects        \\ 
\ IKFT        &  64           & \xmark    & \xmark     & \xmark    &   \xmark   & Commercial catalysts, metals, metal oxides   \\ 
\ LBNL        &  70,012       & \xmark    & \xmark     & \xmark    &   \xmark   & Perovskites precursors, Mn-Sb-O system  \\ 
\midrule
\midrule
\added{\ $\sum$ Labeled}   & \added{2,179}  & \pchk{79}  & \pchk{66}  & \pchk{63}  & \pchk{42} & \added{Partially and fully labeled opXRD data} \\
\added{\ $\sum$ Unlabeled }& \added{90,373} & \xmark     & \xmark     & \xmark     & \xmark    & \added{Unlabeled opXRD data}\\
\bottomrule
\end{NiceTabular}
\end{adjustbox}}
\end{table}

@@

\begin{figure}[!htb]
    \centering
    \includegraphics[width=\linewidth]{figures/hist_CRYSTAL.png}
    \caption{\added{Histograms detailing properties of the structures underlying labeled diffraction patterns in the opXRD database: a) distribution of structures containing specified elements, b) distribution of structures containing spacegroups, c) distribution of number of atoms $N_{\text{atom}}$ contained in unit cell, d) distribution of unit cell volume $V_{\text{uc}}$.}}
    \label{fig:hist_CRYSTAL}
\end{figure}

### 2025-04-29 main.tex
Switch to Wiley Latex Template

\documentclass[a4paper]{article}

@@

%% Language and font encodings
\usepackage{tikz}
\usepackage{tablefootnote}
\usepackage{gensymb}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{csquotes}
\usepackage{doi}
%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
\usepackage{titling}
\usepackage{parskip}

@@

\begin{document}
\maketitle

\textbf{Keywords}: powder x-ray diffraction, machine learning, open-access data, crystal structure determination, phase identification
\begin{abstract}
\input{chapters/00_abstract}
\end{abstract}

@@

\bibliographystyle{bibstyle/bibstyle.bst}
\bibliography{references}

>>>>

\documentclass{WileyMSP-template}

@@

%% Language and font encodings
\usepackage{tikz}
\usepackage{tablefootnote}
\usepackage{gensymb}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{csquotes}
\usepackage{doi}
%% Sets page size and margins
%\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
\usepackage{titling}
\usepackage{parskip}

@@

\begin{document}

\pagestyle{fancy}
\rhead{\includegraphics[width=2.5cm]{vch-logo.png}}

\maketitle

\keywords{powder x-ray diffraction, machine learning, open-access data, crystal structure determination, phase identification}

\begin{abstract}
\input{chapters/00_abstract}
\end{abstract}

@@

\bibliographystyle{bibstyle/MSP}
\bibliography{references}
